MultiDataImportPico

### 2023-12-07 Code/MultiDataImportPico.Rmd
Added more chunk annotations

TargetFile <- "20211223_PICO_MCMIX006_RUN42.csv"

@@

#add ln(value) later

@@

## Create preliminary plot for TargetData

```{r prelim plot}
#Run <- c("MultiCulti/20200124_PICO_MCMIX004_RUN1.csv", "MultiCulti/20200124_PICO_MCMIX006_RUN2.csv")

@@

Pivot_wider to get actinic-lights data aligned with relevant sensor
data. Why are there NULL values in the OD sensor columns? Should always
have a value? Import issue? Misalignment b/t light and OD? Need to
include arrange(Filename, time, Tube) to keep things aligned! Need to
group_by and/or reorder rows appropirately; Be Careful

@@

Actinic light values do not align time wise with OD measures.
Interpolate NA in actinic light columns from last observation, arrange
by MC & Tube Then generate Actinic_par summary column If multiple lights
are activated this chunk will give the summed par of all different
colours for the tube. If a single actinic light is activated per tube,
this gives the par for that tube. Filter rows where !is.na(Actinic_par)
to check for incorrect row sums.

@@

#drop original actinic light columns?
# select(!contains("actinic-lights.light"))

@@

Now that Actinic_par is aligned with each row, coalesce
od-sensors-X.od-720 and od-sensors-X.od-680 into 2 columns, b/c 'Tube'
is already a column, so no need to identify tube X in
od-sensors-X.od-680 columns. This might cause problems later matching OD
measures to actinic light colours. Filter out rows where OD \<= 0

```{r consolidate OD}
TargetDataWide <- TargetDataWide  %>%
   mutate(OD680 = rowSums(.[grep("od-680", names(.))], na.rm = TRUE),
          OD720 = rowSums(.[grep("od-720", names(.))], na.rm = TRUE)) %>%
   select(!contains("od-sensors"))
  # filter(OD680 > 0,
  #        OD720 > 0

#move filtering for OD680 >0 until just before curve fitting to avoid data structure problems
TargetDataWide[1:10,]

@@

rm(TargetDataWide)
```

```{r second prelim plot}

@@

         # OD680 = if_else(OD680 > MovMedian680 + (MovMAD680 * MovAvgScreen) | OD680 < MovMedian680 - (MovMAD680 * MovAvgScreen), MovMedian680, OD680), #consider replacing OD680 and OD720 rather than filter
         # OD720 = if_else(OD720 > MovMedian720 + (MovMAD720 * MovAvgScreen) | OD720 < MovMedian720 - (MovMAD720 * MovAvgScreen), MovMedian720, OD720)

@@

Implement Daily Cumulative PAR for Corrected Actinic by numeric integration

@@

# Save .Rds of Imported Data from TargetFile

```{r save Rds of imported data}
saveRDS(object = TargetDataMetaFilter, file = file.path(DataOut, paste(TargetFileName, "TargetDataMetaFilter.Rds",  sep = "_")), ascii = FALSE, version = NULL,
        compress = "xz", refhook = NULL)
```

>>>>

TargetFile <- "20230210_PICO_MCMIX006_RUN108.csv"

@@

@@

## Create preliminary plot for TargetData
# Plots all OD values. True detection is OD680 and false detection is OD720.
```{r prelim plot}

@@

Pivot_wider to get actinic-lights data aligned with relevant sensor
data. Need to include arrange(Filename, time, Tube) to keep things aligned! Need to
group_by and/or reorder rows appropriately; Be Careful

@@

Actinic light values do not align time wise with OD measures.
Interpolate NA in actinic light columns from last observation, arrange
by MC & Tube Then generate Actinic_par summary column. If multiple lights
are activated, this chunk will give the summed par of all different
colours for the tube. If a single actinic light is activated per tube,
this gives the par for that tube. Filter rows where !is.na(Actinic_par)
to check for incorrect row sums.

@@

@@

Now that Actinic_par is aligned with each row, coalesce
od-sensors-X.od-720 and od-sensors-X.od-680 into 2 columns, b/c 'Tube'
is already a column, so no need to identify tube X in
od-sensors-X.od-680 columns. This might cause problems later matching OD
measures to actinic light colours.

```{r consolidate OD}
TargetDataWide <- TargetDataWide  %>%
   mutate(OD680 = rowSums(.[grep("od-680", names(.))], na.rm = TRUE),
          OD720 = rowSums(.[grep("od-720", names(.))], na.rm = TRUE)) %>%
   select(!contains("od-sensors"))

@@

rm(TargetDataWide)
```
# Prelim plot with culture meta data
```{r second prelim plot}

@@

@@

# Implement Daily Cumulative PAR for Corrected Actinic by numeric integration

@@

# Save compressed .Rds of Imported Data from TargetFile
```{r save Rds of imported data}
saveRDS(object = TargetDataMetaFilter, file = file.path(DataOut, paste(TargetFileName, "TargetDataMetaFilter.Rds",  sep = "_")), ascii = FALSE, version = NULL,
        compress = "xz", refhook = NULL)
```
